Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-28 README.Rmd
fixed some link typos

The [<b>bullet_train</b>](data/bullet_train.csv) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2016 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009]. This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/). It contains comparisons from `r length(unique(c(bullet_train$land_id1, bullet_train$land_id2)))` bullet-land signatures. 12 of the overall 420 lands (6 lands per bullets, 35 bullets in each set) are excluded from the comparison. Six of these lands show so-called "tank rash" - damage to the bullets after it exited the barrel (see [tank rash scans](LEAscans/tankrash.md)). Another bullet (Bullet E from Hamby 173) is excluded because it could not be matched visually to the barrel it was supposedly from (see [scans from bullet E](LEAscans/bullete.md)).

[<b>bullet_train</b>](data/bullet_train.csv) is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip). The steps taken to create **bullet_train** from the raw data are found [here](code/02-data-preparation.Rmd). These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.

@@

[**bullet-test.csv**](data/bullet_test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Similar to the training set, each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. [**bullet-test.csv**](data/bullet_test.csv.zip) is generated from the raw versions of the data found [here](data/raw/h224-set1-features.rds.zip) and [here](data/raw/h224-set11-features.rds.zip). The variables in the test data are the same as the training data described above.

@@

- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to 'Signature 1' or 'Signature 2'
- `r names(signatures)[2]`: the (relative) x position of the signature (in microns)
- `r names(signatures)[3]`: the (relative) y position of the signature height (in microns)

>>>>

The [<b>bullet_train</b>](data/bullet_train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2016 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009]. This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/). It contains comparisons from `r length(unique(c(bullet_train$land_id1, bullet_train$land_id2)))` bullet-land signatures. 12 of the overall 420 lands (6 lands per bullets, 35 bullets in each set) are excluded from the comparison. Six of these lands show so-called "tank rash" - damage to the bullets after it exited the barrel (see [tank rash scans](LEAscans/tankrash.md)). Another bullet (Bullet E from Hamby 173) is excluded because it could not be matched visually to the barrel it was supposedly from (see [scans from bullet E](LEAscans/bullete.md)).

**bullet_train** is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip). The steps taken to create **bullet_train** from the raw data are found [here](code/02-data-preparation.Rmd). These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.

@@

[**bullet-test.csv**](data/bullet-test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Similar to the training set, each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. **bullet-test.csv** is generated from the raw versions of the data found [here](data/raw/h224-set1-features.rds.zip) and [here](data/raw/h224-set11-features.rds.zip). The variables in the test data are the same as the training data described above.

@@

- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to "Signature 1" or "Signature 2".
- `r names(signatures)[2]`: The (relative) x position of the signature (in microns).
- `r names(signatures)[3]`: The (relative) y position of the signature height (in microns).
